Plot Figures for McDuffie et al., 2023 (those generated in R)

### 2023-08-14 analysis/Manuscript/Paper_RFigures.Rmd
Figure 3 updates

  # Figure SX

  p1 <-  ggplot(cResultslong, aes(x=SuperRegion, y=mean))+
        geom_linerange(aes(x=SuperRegion,ymin=`2.5%`, ymax=`97.5%`,group=discount.rate),
                       color = 'lightgray',size=1,
                       position = position_dodge(0.8))+
        geom_point(aes(color = discount.rate), position = position_dodge(0.8),size=2)+
        coord_flip()+
        scale_color_brewer('Discount Rate',palette = 'Spectral',direction=-1)+
        scale_x_discrete(labels = function(x) str_wrap(x,width=30))+
        scale_y_continuous(limits=c(0,3000), label = scales::dollar)+
        xlab("")+ylab("$(2020)/mT" ~CH[4])+
        ggtitle(paste0('Net Present Damages per metric ton methane \nby GBD Super Region'))+
        theme_minimal()+
        theme(legend.position = c(0.7,0.4),
              legend.title=element_text(size=16), 
              legend.text=element_text(size=16))+
        theme(axis.text = element_text(size=16),
              axis.title = element_text(size=16))
# Figure 2c
p2 <-  cResultslong %>%
        filter(discount.rate == '2.0% Ramsey') %>%
        ggplot(aes(x=SuperRegion, y=mean,fill = SuperRegion))+
        geom_bar(stat = 'identity', position = 'dodge',width=0.6)+
        geom_pointrange(aes(x=SuperRegion,ymin=`2.5%`, ymax=`97.5%`),
                        position = position_dodge(width=0.2),size=0.3,alpha=0.8)+#errobar,width = 0.4)+
        coord_flip()+
        scale_fill_brewer(palette = 'Spectral',direction=-1)+
        scale_x_discrete(labels = function(x) str_wrap(x,width=30))+
        scale_y_continuous(limits=c(0,3000), label = scales::dollar)+
        xlab("")+ylab("$(2020)/mT" ~CH[4])+
        ggtitle(paste0('Damages per metric ton methane \nby GBD Super Region'))+
        theme_minimal()+
        theme(legend.position = 'none')+#c(0.7,0.3))+
        theme(axis.text = element_text(size=16),
              axis.title = element_text(size=16))+
        geom_text(data=means%>%filter(discount.rate == '2.0% Ramsey'),
            aes(y=means, x=SuperRegion,
                label=paste0('$', round(means, 2)), vjust=-0.35,hjust = -0.35),
            color    = 'grey20',
            size     = 6)
p2

@@

#Socioeconomic results - from RFT code
Results2 <- file.path(rft_inputs,'npd_global_rff_means_NOx_1_MMM.csv')
rft_results <- read_csv(Results2, col_types = cols())

@@

p1 <- plot_data %>%
  mutate(subgroup_col = (fct_relevel(subgroup_col, '3.0% CDR',
                                     "2.0% CDR","3.0% Ramsey",
                                     "2.5% Ramsey","1.5% Ramsey",
                                     "MIROC","GISS","GFDL",
                                     "CESM2","HadGEM",
                                     '-50% NOx','+50% NOx',
                                     "SocioEcon. Lower","SocioEcon. Upper",
                                     "CRF Lower","CRF Upper"
                                     ))) %>%
  ggplot( aes(x=(subgroup_col), y=(val_col),fill=group_col))+
  geom_bar(stat='identity',width = 0.4)+
  #scale_fill_brewer() (palette = 'Spectral',direction=-1)+
  scale_fill_manual(name = '',values=c(brewer.pal(11,"Spectral")[c(2,4,8,10,11)]),
  breaks= c('CRF (95% CI)','Socioeconomics (95% CI)','NOx Emissions (\u0394 50%)','GCM (mean)','Discount Rate (mean)'))+
  coord_flip()+
  theme_minimal()+
  xlab('')+
  ylab("Change in Global $1700(2020)/mT" ~CH[4])+
  theme(axis.text = element_text(size=16),
        axis.title = element_text(size=16))+
  scale_y_continuous(limits = c(-1000, 1300),label = scales::dollar)+
  theme(legend.position = c(0.8,0.25),
        legend.title=element_text(size=14), 
        legend.text=element_text(size=14))

>>>>

  # Figure S7

  p1 <-  ggplot(cResultslong, aes(x=SuperRegion, y=mean))+
        geom_linerange(aes(x=SuperRegion,ymin=`2.5%`, ymax=`97.5%`,group=discount.rate),
                       color = 'lightgray',size=1,
                       position = position_dodge(0.8))+
        geom_point(aes(color = discount.rate), position = position_dodge(0.8),size=2)+
        coord_flip()+
        scale_color_brewer('Discount Rate',palette = 'Spectral',direction=-1)+
        scale_x_discrete(labels = function(x) str_wrap(x,width=30))+
        scale_y_continuous(limits=c(0,3200), label = scales::dollar)+
        xlab("")+ylab("$(2020)/mT" ~CH[4])+
        ggtitle(paste0('Net Present Damages per metric ton methane \nby GBD Super Region'))+
        theme_minimal()+
        theme(legend.position = c(0.7,0.4),
              legend.title=element_text(size=16), 
              legend.text=element_text(size=16))+
        theme(axis.text = element_text(size=16),
              axis.title = element_text(size=16))
  p1

# Figure 2c
p2 <-  cResultslong %>%
        filter(discount.rate == '2.0% Ramsey') %>%
        ggplot(aes(x=SuperRegion, y=mean,fill = SuperRegion))+
        geom_bar(stat = 'identity', position = 'dodge',width=0.6)+
        geom_pointrange(aes(x=SuperRegion,ymin=`2.5%`, ymax=`97.5%`),
                        position = position_dodge(width=0.2),size=0.3,alpha=0.8)+#errobar,width = 0.4)+
        coord_flip()+
        scale_fill_brewer(palette = 'Spectral',direction=-1)+
        scale_x_discrete(labels = function(x) str_wrap(x,width=30))+
        scale_y_continuous(limits=c(0,3000), label = scales::dollar)+
        xlab("")+ylab("$(2020)/mT" ~CH[4])+
        ggtitle(paste0('Damages per metric ton methane \nby GBD Super Region'))+
        theme_minimal()+
        theme(legend.position = 'none')+#c(0.7,0.3))+
        theme(axis.text = element_text(size=16),
              axis.title = element_text(size=16))+
        geom_text(data=means%>%filter(discount.rate == '2.0% Ramsey'),
            aes(y=means, x=SuperRegion,
                label=paste0('$', round(means, 2)), vjust=-0.35,hjust = -0.35),
            color    = 'grey20',
            size     = 6)
p2

@@

#Socioeconomic results - from RFT code
Results2 <- file.path(rft_inputs,'npd_global_rff_means_vsl10_NOx_1_MMM.csv')
rft_results <- read_csv(Results2, col_types = cols())

@@

p1 <- plot_data %>%
  mutate(subgroup_col = (fct_relevel(subgroup_col, '3.0% CDR',
                                     "2.0% CDR","3.0% Ramsey",
                                     "2.5% Ramsey","1.5% Ramsey",
                                     "MIROC","GISS","GFDL",
                                     "CESM2","HadGEM",
                                     '-50% NOx','+50% NOx',
                                     "SocioEcon. Lower","SocioEcon. Upper",
                                     "CRF Lower","CRF Upper"
                                     ))) %>%
  ggplot( aes(x=(subgroup_col), y=(val_col),fill=group_col))+
  geom_bar(stat='identity',width = 0.4)+
  #scale_fill_brewer() (palette = 'Spectral',direction=-1)+
  scale_fill_manual(name = '',values=c(brewer.pal(11,"Spectral")[c(2,4,8,10,11)]),
  breaks= c('CRF (95% CI)','Socioeconomics (95% CI)','NOx Emissions (\u0394 50%)','GCM (mean)','Discount Rate (mean)'))+
  coord_flip()+
  theme_minimal()+
  xlab('')+
  ylab("Change in Global $1800(2020)/mT" ~CH[4])+
  theme(axis.text = element_text(size=16),
        axis.title = element_text(size=16))+
  scale_y_continuous(limits = c(-1100, 1300),label = scales::dollar)+
  theme(legend.position = c(0.8,0.25),
        legend.title=element_text(size=14), 
        legend.text=element_text(size=14))
